kableExtraTutorial

### 2017-09-19 rmd_tutorial.rmd
changes to rmd

```{r setup, echo=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)

#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

@@

```{r, echo=FALSE}
##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

>>>>

discription of data and report here

```{r setup, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)

setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

@@

```{r, echo=FALSE}
#todo, remove bottom axis
##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)
